### 2022-01-16 input/experiments.tex
meow

%% This section describes the results of our experimentation evaluating
%% the properties of \NAME that enables adaptive scoped broadcast in
%% dynamic networks.

%% \TODO{Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
%% |V|))$, and generates messages of identical space complexity. In terms
%% of number messages, in the average case, a \process $x$ chosen
%% uniformly at random among all \processes creates a logical
%% partition. Its messages $\alpha_x$ spread through the network until
%% reaching \processes that belong to another partition closer to
%% them. This splits partitions in half on average. Overall, the $n^{th}$
%% new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
%%       \log_2 n \rfloor}})$} \processes. This decreases every new
%% partition until reaching one \process per new partition: its
%% source. The average number of messages per \process is
%% \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
%%       \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
%% number of neighbors per \process.}
%% \TODO{\TODO{Multiple receipt and multiple delivery} In terms of number of
%% messages, deleting the $a^{th}$ partition generates twice as many
%% messages as creating the $a^{th}$ partition: $\delta$ messages travel
%% through the partition, then $\alpha$ messages compete to fill the gap
%% \TODO{which is?}. \TODO{What about false positives?} Overall, the
%% communication complexity shows that \NAME scales well to the number of
%% partitions.}

%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.

@@

\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of traffic and termination time.

@@

\noindent We focus on the complexity of \NAME. We measure the average
number of messages generated per \process per second during the
experiment; and the time before reaching consistent partitioning after
adding or removing a partition.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are more expensive than add operations. Indeed, the
top part of the figure shows that after 21 seconds, when the
experiment involves removals, traffic includes both $\alpha$'s and
$\delta$'s. The latter aims at removing stale information and
triggering competition while the former aims at updating shortest
paths. As corollary, the convergence time increases, for $\delta$
messages must reach the partition borders before sound competitors
propagate their partition. It is worth noting that this delete
operation involves concurrency: removals still propagate while
the competition has started. %%is already partially triggered and propagating.

%% \begin{figure*}
%%   \begin{center}
%%     \subfloat[Part A][\label{fig:complexity}Overhead of consistent partitioning
%%       using \NAME]
%%              {\includegraphics[width=0.5\columnwidth]{img/as_cast_complexity.eps}}
%%              \hfill
%%     \subfloat[Part B][\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.]
%%              {\includegraphics[width=0.5\columnwidth]{img/as_cast_geant.eps}}
%%   \end{center}
%% \end{figure*}

@@

%% \subsection{Distribution and hotspots}

%% \subsection{Confirm that \NAME locks down the traffic of decentralized content
%%   indexing in the context of dynamic inter-autonomous system
%%   communications.}

@@

We build a network by duplicating the G{\'E}ANT
topology~\cite{knight2011internet} -- a real infrastructure spanning
across Europe -- and by connecting these two clusters with a high
latency link: $200$ ms simulating cross-continental communications
such as Europe-America. The experiments comprise $2 \times 271 = 542$
\processes and we derive intra-cluster latency from their \processes'
geographic location.

@@

  \item[Description:] We build a network of networks by using an Edge
    infrastructure comprising 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet} as depicted in the left
    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
    the figure) link autonomous systems together, \eg a Lisbon \node
    links Portugal to Spain and United Kingdoms through a Madrid \node
    and a London \node respectively.

    \noindent The left Figure~\ref{fig:europe-ases} depicts the
    operations executed during the simulation that lasts 7 seconds: at
    1 second, a \node located in Lisbon, Portugal performs an
    \texttt{Add}; at 2 seconds, a \node located in Palma de Majorque,
    Spain performs an \texttt{Add}; at 3 seconds, a \node located in
    Paris, France performs an \texttt{Add}; at 4 seconds, a \node
    located in Hvanneyri, Iceland performs an \texttt{Add}; and
    finally, at 5 seconds, the \node in Spain performs a \texttt{Del}.

    \noindent \NAMEC extends \NAME to enable lazy dynamic partitioning
    by allowing gateways to stop notifications when their respective
    network does not appear to have a source. Using \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous systems, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.

    \noindent We measure the number of messages transiting through the
    network for each operation, and we measure the number of
    \processes that index (\ie belong to a partition) over time.

  \item[Results:] Figure~\ref{fig:europe-ases} shows the results
    of this experiment. The top part highlights the cost of each
    partitioning protocol after each operation, while the bottom part
    provides the insight that explains these costs by displaying the
    number of indexes maintained by each protocol.

@@

    \noindent Figure~\ref{fig:europe-ases} shows that Spain's
    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
    \process in Madrid links Portugal to Spain and the rest of
    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
    is, only 11 \processes in Spain actually need to receive and
    deliver the new notification, hence the small overhead of this
    operation with \NAME. Using \NAMEC, the overhead is slightly
    higher since
    \begin{inparaenum}[(i)]
    \item the 20 \processes of Spain's network need to receive and
      deliver the new notification, \emph{and}
    \item Madrid's \process echoes Lisbon's notification as soon as it
      receives Palma's notification to 11 \processes.
    \end{inparaenum}

@@

\TODO{Overall + transition.}

>>>>

@@

\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

\noindent We measure the average number of messages generated per
\process per second; and the time before reaching consistent
partitioning after adding or removing a partition.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as \texttt{Add}
operations. Indeed, the top part of the figure shows that after 21
seconds, when the experiment involves removals, traffic includes both
$\alpha$'s and $\delta$'s. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started. %%is already partially triggered and
propagating.

@@

@@

We build a network by duplicating the G{\'E}ANT
topology~\cite{knight2011internet} -- an infrastructure of 271 \nodes
spanning across Europe -- and we link these two clusters with a high
latency link: $200$ ms simulating cross-continental communications
such as Europe-America. The experiments comprise $2 \times 271 = 542$
\processes and we derive intra-cluster latency from their \processes'
geographic location.

@@

  \item[Description:] We build a network of networks by using another
    Edge infrastructure comprising 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet} as depicted in the left
    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
    the figure) link autonomous systems together, \eg a Lisbon \node
    links Portugal to Spain and United Kingdoms through a Madrid \node
    and a London \node respectively.

    \noindent The left Figure~\ref{fig:europe-ases} depicts the
    operations executed during the simulation that lasts 7 seconds: at
    1 second, a \node located in Lisbon, Portugal performs an
    \texttt{Add}; at 2 seconds, a \node located in Palma de Majorque,
    Spain performs an \texttt{Add}; at 3 seconds, a \node located in
    Paris, France performs an \texttt{Add}; at 4 seconds, a \node
    located in Hvanneyri, Iceland performs an \texttt{Add};
    finally at 5 seconds, the \node in Spain performs a \texttt{Del}.

    \noindent We evaluate \NAME against an extension of \NAME called
    \NAMEC that enables lazy dynamic partitioning by allowing gateways
    to stop notifications when their respective network does not
    appear to have a source. Using \NAMEC, each \process maintains a
    \emph{local} index that corresponds to the best partition of its
    autonomous systems, and a \emph{global} index that corresponds to
    the best partition cross autonomous systems, \ie adjacent
    autonomous systems that have at least one source.

    \noindent We measure the number of messages transiting through the
    network for each operation, and we measure the number of
    \processes that maintain an index (\ie that belong to a partition)
    over time.

  \item[Results:] The right of Figure~\ref{fig:europe-ases} shows the
    results of this experiment. The top part highlights the cost of
    each partitioning protocol after each operation, while the bottom
    part provides the insight that explains these costs by displaying
    the number of indexes maintained by each protocol.

@@

    \noindent Figure~\ref{fig:europe-ases} shows that Spain's
    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
    gateway in Madrid links Portugal to Spain and the rest of
    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
    is, only 11 \processes in Spain actually need to receive and
    deliver the new notification, hence the small overhead of this
    operation with \NAME. Using \NAMEC, the overhead is slightly
    higher since
    \begin{inparaenum}[(i)]
    \item the 20 \processes of Spain's network need to receive and
      deliver the new notification, \emph{and}
    \item Madrid's gateway echoes Lisbon's notification as soon as it
      receives Palma's notification to 11 \processes.
    \end{inparaenum}

@@

\begin{asparadesc}
  \item[Overall,] these experiments highlight the scalability of \NAME
    and \NAMEC in dynamic networks such as Edge infrastructures. Next
    Section reviews state-of-the-art approaches designed to index
    content in geo-distributed infrastructures.
\end{asparadesc}

% \TODO{Overall + transition.}
